% resume.tex
%
% (c) 2002 Matthew M. Boedicker <mboedick@mboedick.org> http://mboedick.org
% $Id: resume.tex,v 1.7 2004/02/02 14:21:06 mboedick Exp $
%
\documentclass[10pt]{article}
\renewcommand{\labelitemii}{}
\usepackage[top=.1 in, left=0.3 in, bottom=0.2 in, right=0.3 in]{geometry}
\usepackage{setspace}
\textheight=10.2in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\itemsep}{5in}
\setlength{\partopsep}{-1ex}
\setlength{\topsep}{0in}
\addtolength{\parsep}{0ex}
\usepackage{mdwlist}
\singlespace
%\addtolength{\textheight}{-0.1in}




\begin{document}

%\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
%\textbf {\large Guojun Zhu}  & \\
%2112 S Orchard St., Apt. 302  & 217-384-0692 \\
%Urbana, IL, 61801 & gzhu1@uiuc.edu \\
%\end{tabular*}

\begin{center}
\textbf{\Large Guojun Zhu}

\rule[0.6ex]{\textwidth}{0.4pt} \\
\raisebox{0.2ex}{801 E Michigan Ave., Urbana, IL, 61801 $\bullet$ 217-6891348 $\bullet$ gzhu1@illinois.edu}
\end{center}
%\vspace{0.2in}
%{\large \textbf{Objective}}
%
%\hspace{6ex}Seeking position of quantitative research and financial engineering in financial institutions. 
\hrulefill\\
\vspace{0.12in}
{\large \textbf{Education}}

	\begin{itemize}
	\item[] \textbf{University of Illinois at Urbana-Champaign}{\hfill}Urbana, IL \\
	\vspace{1ex}
	 %\begin{tabular*}{5.7in}{l@{\extracolsep{\fill}}r}
		\textbf{ Ph.D,  Theoretical Condensed Matter Physics}, \emph{Jan. 2011} {\hfill}GPA: \emph{3.85}/4.0\\		 
		\begin{itemize*}
			\item[-]Thesis topic: Thermodynamic Properties and Narrow Feshbach Resonance of the Ultra-cold Fermionic Atoms;
			\item[-]Developed theoretical model for 3-hyperfine-species cold Fermion gas by extending Leggett's BCS-BEC crossover model,  
			\item[-]Analyzed the model with numeric methods (finite difference, Monte Carlo).
		\end{itemize*}
		 		%\hline	
		%\end{tabular*}
		\textbf{ M.S., Finance}, {May 2006}\hfill GPA: {3.85}/4.0\\

	 \begin{itemize}
	 \item Relevant coursework: {econometrics, continuous-time finance, financial engineering I/II, hedge fund, investment banking, monetary policy, corporate finance, etc}.
		\end{itemize}

	\textbf{ M.S., Physics}, Dec. 2002{\hfill} GPA: 3.97/4.0\\
	\vspace{0.1in}
	%Courses already taken: \emph{microeconomics, macroeconomics, econometrics, statistics,}&\\
	%\emph{\hspace{6ex} investment, financial derivatives, financial engineering, investment banking}&\\
	 %Courses in progress: \emph{ corporation finance, behavior finance}&\\ 
	%	\end{description}
	 % &\\
  \item[]\textbf{University of Science and Technology of China}{\hfill} Hefei, Anhui, China\\
		\textbf{ B.S., Physics}, May 2001{\hfill}GPA: 3.8/4.0
	\end{itemize}

%\pagebreak[5]
%\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
%\textbf {\large Guojun Zhu}  & \\
%2112 S Orchard St., Apt. 302  & 217-384-0692 \\
%Urbana, IL, 61801 & gzhu1@uiuc.edu \\
%\end{tabular*}
%\\
\hrulefill\\
\vspace{0.12in}
{\large \textbf{Skills}}

\begin{description*}
%\item[Finance:]I have gained and am still gaining solid finance knowledge in MSF (Master of Science, Finance) program; and I am very glad that they were put into real use successfully during my internship in summer 2005.   
\item[Mathematics:]
modern probability theory, statistics, stochastic calculus, partial differential equation, Monte Carlo simulation,  finite difference;  
\item[Computer Languages:]
 Java, C, C++, C\#, Perl, SQL, HTML,  ASP,  R, Pascal,  Fortran, VBA, Basic;
 \item[Development Techniques:]
Spring, Hibernate, Ajax, Mysql, JavaEE,  JSP, Struts;
\item[Software Applications:]
Excel,  Matlab, Mathematica, \LaTeX;
\item[Languages:]
fluent in English and Chinese.

\end{description*}
\hrulefill\\
\vspace{0.12in}
{\large \textbf{Sample Projects}}

\begin{itemize*}
\item[-] Networked environment for music analysis ({http://nema.lis.uiuc.edu/diy}, Spring/Ajax/Hibernate/Mysql, 20K+ lines)
\item[-] Digital information risk analysis system ({http://sulfite.lis.uiuc.edu:8080/InformProject}, Struts/Spring/Ajax/Mysql, 10K+ lines);
\item[-] Mini library for pricing vanilla and exotic equality options with binomial tree, Monte Carlo, finite difference methods (C++, 2K+ lines);
\item[-] Aggregating academic papers from different internet-based databases and providing uniform web-based searching service (Java/JSP/Perl);
\item[-] Multi-factor long-short risk-neutral stock selection model (R);
\item[-] Term structure building and interest swap pricing (Excel); 
\item[-] Numerically solution of the BCS-BEC crossover gap equation (Mathematica).
\end{itemize*}
\hrulefill\\
\vspace{0.12in}
{\large \textbf{Experience}}

	\begin{itemize}

		 \item[]
			\textbf{University of Illinois at Urbana-Champaign}{\hfill} Urbana, IL\\
			Research Programmer{\hfill}June 2008 - Present\\			
		%\vspace{0.3ex}
		
			\begin{itemize*}
				\item[-] Developed web applications for various digital information retrieval and analysis projects;
				\item[-] Designed data access modular, business logic, administrative modular and miscellenous parts;
				\item[-] Leveraged various techniques: struts, spring, hibernate, ajax framework (dojo, prototype), core design patterns, etc. 
	    \end{itemize*}
	    Teaching Assistant{\hfill}Aug. 2001 - June 2008\\			
		%\vspace{0.3ex}
		
			\begin{itemize*}
				\item[-] Lead discussion/lab sections of physics 101/211 in several semesters;
				\item[-] Was honored in \emph{Daily Illini}'s list of ``\textbf{Teachers Ranked as Excellent by their Students}'' for spring 2005 (Physics 101), Spring 2007 (Physics 211).
	    \end{itemize*}
			\item[]
			\textbf{Illinois Business Consulting} {\hfill}Chicago, IL\\
			Consultant{\hfill}Jan. 2006 \\			
		
		%\vspace{.5ex}
		%Job Responsibility:
			\begin{itemize*}
				\item[-] Worked in a two-person team  at \textbf{Towers Perrin};
				\item[-] Developed and analysize tentative cognitive/functional test battery of elderly people for life insurance underwriting.
				%\item[-] Searched for functional and cognitive tests possibly useful in life insurance underwriting for elderly people;
				%\item[-] Made cost vs. benefit analysis about tests and recommended a set of tests for underwriting.
			\end{itemize*}
	 \item[]
			\textbf{Capital Hunter } {\hfill} San Diego, CA\\
			Financial Analyst \& Technology Specialist{\hfill}June 2005 - Aug. 2005 \\			
		
		%\vspace{.5ex}
		%Job Responsibility:
			\begin{itemize*}
				\item[-] Analyzed everyday financial data about venture capital and private equity financing;
				\item[-] Compiled regional quarterly reports on venture capital and private equity financing.
			\end{itemize*}
		
%	\begin{itemize}
%		\item designed and implemented data exchange architectures using XML, Python, and Java
%		\item developed, documented and maintained search engine technologies using Python and C
%	\end{itemize}


	    
%	\begin{itemize}
%		\item designed and implemented data exchange architectures using XML, Python, and Java
%		\item developed, documented and maintained search engine technologies using Python and C
%	\end{itemize}

 \end{itemize}

\end{document}
