% !TeX root =thesis.tex
%\subsection{Path integral approach for single channel\label{sec:pathInt}}
\label{sec:pathInt}
Randeria and the company has studied this problem with path integral and it is proved to be a rather nice tool for the problem due to its flexibility and readiness for extension to higher order fluctuation.  

We start with an attractive $\delta$-potential in real space.  This is not equivalent to the l reduced pairing potential as in original BCS work.  However, reduced paring potential only couples  particles of the opposite momentum and does not support simple form of Hubbard-Stratonovich transformation, which is essential to solve the problem in path integral formulation.  
\begin{equation}
\hat{H}-\mu\hat{N}=\sum_{\sigma}\int{d^{d}r}c^{\dagger}_{\sigma}(\vr)\br{-\nth{2m}\nabla^{2}-\mu}c^{}_{\sigma}(\vr)-g\int{d^{d}r}c^{\dagger}_{\uparrow}(\vr)c^{\dagger}_{\downarrow}(\vr)c^{}_{\downarrow}(\vr)c^{}_{\uparrow}(\vr)
\end{equation}
 We can write down the action for the quantum partition function $\mathcal{Z}=\int{D(\bar\psi,\psi)\exp\br{-S[\bar\psi,\psi]}}$
\begin{equation}
S[\bar\psi,\psi]=\int^{\beta}_{0}d\tau\int{d^{d}r}\mbr{\sum_{\sigma}\bar\psi_{\sigma}(\vr,\tau)\br{\partial_{\tau}-\nth{2m}\nabla^{2}-\mu}\psi_{\sigma}(\vr,\tau)-g\bar\psi_{\uparrow}(\vr,\tau)\bar\psi_{\downarrow}(\vr,\tau)\psi^{}_{\downarrow}(\vr,\tau)\psi^{}_{\uparrow}(\vr,\tau)}
\end{equation}
We try to solve this system by introduce Hubbard-Stratonovich transformation.   Introduce a bosonic field $\Delta(\vr,\tau)$ coupled with Cooper channel $\psi(\vr,\tau)\psi(\vr,\tau)$. %Here we follow the normal notation from path integral, $r$ is four tempo-space coordinator.  
We write down first the Gaussian integral of $\Delta$
\begin{equation}
1=\int{D(\bar\Delta,\Delta)}\exp\br{-\nth{g}\int{d\tau{d}^{d}r}\bar\Delta\Delta}
\end{equation}
Note that we absorb the extra constant of integration into the measure of $D(\bar\Delta,\Delta)$.
And with a shift of $\Delta(\vr,\tau)\rightarrow\Delta(\vr,\tau)-g\psi(\vr,\tau)\psi(\vr,\tau)$, we have 
\footnote{$\int{D(\bar\Delta,\Delta)}\cdot1$ is only a constant factor on partition function $\mathcal{Z}$ and has no effect on real physical quantity, therefore, we can take it as 1, (equivalently divide the $\mathcal{Z}$ by a constant)}
\begin{equation}
\exp\br{g\int{d\tau{}d^{d}r}\psi_{\uparrow}\bar\psi_{\downarrow}\psi_{\downarrow}\psi_{\uparrow}}=
\int{D(\bar\Delta,\Delta)}\exp\bbr{-\int{d\tau{d^{d}r}}\mbr{\nth{g}\abs{\Delta}^{2}-\br{\bar\Delta\psi_{\downarrow}\psi_{\uparrow}+\Delta\bar\psi_{\uparrow}\bar\psi_{\downarrow}}}}
\end{equation}
Now the interaction term can be replaced.
\begin{equation*}
\mathcal{Z}=\int{D(\bar\psi,\psi)\int{D(\bar\Delta,\Delta)}\exp\bbr{-\int{d\tau{d^{d}r}}\mbr{\sum_{\sigma}\bar\psi_{\sigma}\br{\partial_{\tau}-\nth{2m}\nabla^{2}-\mu}\psi_{\sigma}+\nth{g}\abs{\Delta}^{2}-\br{\bar\Delta\psi_{\downarrow}\psi_{\uparrow}+\Delta\bar\psi_{\uparrow}\bar\psi_{\downarrow}}}}}
\end{equation*}
This form is bilinear to $\psi$, and we can rewrite it into a nicer form in Nambu spinor representation
\begin{equation}
\bar\Psi=\begin{pmatrix}\bar{\psi}_{\uparrow}&\psi_{\downarrow}\end{pmatrix}\text{,  }\qquad
\Psi=\begin{pmatrix}{\psi}_{\uparrow}\\\bar\psi_{\downarrow}\end{pmatrix}
\end{equation}
\begin{equation}
\mathcal{Z}=\int{D(\bar\psi,\psi)}\int{D(\bar\Delta,\Delta)}\exp
	\bbr{-\int{d\tau{d^{d}r}}\mbr{\nth{g}\abs{\Delta}^{2}-\bar\Psi \nG\Psi}}
\end{equation}
where 
\begin{equation}\label{eq:pathInt:nG}
\nG=\begin{pmatrix}
[\hat{G}_{0}^{(p)}]^{-1}&\Delta\\\bar\Delta&[\hat{G}_{0}^{(h)}]^{-1}
\end{pmatrix}
\end{equation}
is known as Gor'kov Green function, and $[\hat{G}_{0}^{(p)}]^{-1}=-\partial_{\tau}+\nth{2m}\nabla^{2}+\mu$, and $[\hat{G}_{0}^{(h)}]^{-1}=-\partial_{\tau}-\nth{2m}\nabla^{2}-\mu$ represent the non-interacting Green functions of the particle and hole respectively. Now $\Psi$ can be integrated out formally and partition function then only depends on bosonic field $\Delta$.
\begin{equation}\label{eq:pathInt:DeltaPF}
\mathcal{Z}=\int{D(\bar\Delta,\Delta)}\exp
	\bbr{-\mbr{\br{\int{d\tau{d^{d}r}}\nth{g}{\bar\Delta\Delta}}-\ln\det\nG}}
\end{equation}
And action is
\begin{equation}\label{eq:pathInt:DeltaAction}
S[\bar\Delta,\Delta]=
	{\mbr{\br{\int{d\tau{d^{d}r}}\nth{g}{\bar\Delta\Delta}}-\ln\det\nG}}
\end{equation}
Note that $\ln\det\nG$ goes through both the normal space and $2\times2$ Nambu spinor space.  

\subsection{Mean field result\label{sec:pathInt:meanfield}}
The saddle point equation of Eq. (\ref{eq:pathInt:DeltaPF}) gives the mean-field result of the system.  First we need to find the derivative of $\ln\det\nG$.  We notice the identity
\begin{equation}
\ln\det\hat{A}=\tr\ln\hat{A}
\end{equation}
and differential rule of a function like $\tr\ln$
\begin{equation}\label{eq:pathInt:diffTr}
\frac{\delta}{\delta\phi_q}\tr\ln(\nG)=\tr(\hat{\mathcal{G}}\frac{\delta}{\delta\phi_q}\nG)
\end{equation}
The saddle equation of Eq. (\ref{eq:pathInt:DeltaPF}) (differential with respect to $\Delta$) is
\begin{equation}
\nth{g}\bar{\Delta}(\vr,\tau)-\tr\mbr{\hat{\mathcal{G}}(\vr,\tau,\vr,\tau)\begin{pmatrix}0&1\\0&0\end{pmatrix}}=0
\end{equation}
Here this matrix is in the Nambu Spinor space.  If we seek a tempo-spacial homogeneous solution of $\Delta_0$, we can find the Nambu Green function from Eq. (\ref{eq:pathInt:nG}) in momentum space
\begin{equation}\label{eq:pathInt:G0}
G_0(p)=\nth{(i\omega_n)^2-E_\vp^2}
\begin{pmatrix}
	i\omega_n+\xi_\vp&-\Delta_0\\
	-\bar{\Delta}_0&i\omega_n-\xi_\vp
\end{pmatrix}
\end{equation}
Here $\omega_n$ is Matsubara frequency of Fermions.  $\xi_{\vk}=\epsilon_{\vk}-\mu$, $\epsilon_{\vk}=\vk^{2}/2m$,  $E_\vp=\sqrt{\xi_\vp^2+\abs{\Delta_0}^2}$.  And the saddle point equation can be rewritten as 
\begin{equation}
\nth{g}\bar{\Delta}_0=\frac{T}{L^d}\sum_{\vp,n}\frac{\bar\Delta_0}{\omega_n^2+E_\vp^2}
\end{equation}
The summation of Matsubara frequency can be evaluated and we find 
\begin{equation}
\nth{g}=\nth{L^d}\sum_{\vp}\frac{1-2n_f(E_p)}{2E_p}=\nth{L^d}\sum_{\vp}\frac{\tanh{(E_p/2T)}}{2E_p}
\label{eq:pathInt:gap}
\end{equation}
where $n_f(\epsilon)$ is the fermi distribution function.  This is exactly the gap equation obtained from other methods as well.  On the other hand, $\nG$ in Eq. (\ref{eq:pathInt:nG})  is the inverse of fermion-fermion correlation of $\Psi$.  In mean field, $G_{0}$ as Eq. (\ref{eq:pathInt:G0}) can be diagnosed in momentum space with a canonical (Bogoliubov) transformation.  Nevertheless, poles is where  $\omega^2-E_\vp^2=0$ (with a analytic continue of $i\omega_{n}\rightarrow\omega+0^{+}$) as we can see from  Eq. (\ref{eq:pathInt:G0}) and therefore the spectrum of fermionic excitation is $\pm{}E_{p}$.  

Summand in Eq. \ref{eq:pathInt:gap} does not decreases fast enough in 3D and the summation does not converges.  This is because our assumption of contact interaction breaks down when reaching real potential range $a_{c}$, i.e., the summation of momentum is capped at some high momentum $\Lambda$ related to $1/a_{c}$.  Notice that in 3-D, we have a relation that connect the bare potential $g$ to more physically observable s-wave scattering length $a_{s}$
\begin{equation}\label{eq:pathInt:as}
\frac{m}{4\pi{}a_{s}}=-\nth{g}+\sum_{k<\Lambda}\nth{2\epsilon_{\vk}}
\end{equation}
We can renormalize Eq. \ref{eq:pathInt:gap} with this relation
\begin{equation}
-\frac{m}{4\pi{}a_{s}}=\sum_{\vk}\mbr{\frac{\tanh{(E_k/2T)}}{2E_k}-\nth{2\epsilon_{\vk}}}
\end{equation}
Now the gap equation has proper decay in high momentum and no artificial cutoff is necessary.  There are two unknown parameters, $\mu$ and $\Delta$,  in the equation.  We need another equation in order to pin them down. To compliment the gap equation, we can introduce the number equation, $n=-\partial\Omega/\partial\mu$. At the saddle point, the thermodynamic potential is $\Omega_{0}=S[\Delta_{0}]/\beta$, and we have number equation
\begin{equation*}
n=-\nth{\beta}\tr\br{{G_{0}\pdiff{G_{0}^{-1}}{\mu}}}
\end{equation*}
similarly the summation over the Mastubara frequency can be evaluated and we have equation
\begin{equation}
n=\nth{L^{d}}\sum_{\vk}\mbr{1-\frac{\epsilon_{\vk}}{E_{\vk}}\tanh{(\frac{E_{\vk}}{2T})}}
\end{equation}

\subsection{Gaussian fluctuation and collective mode}\label{sec:collective1}
Once the mean field value is obtained, we can expand partition function Eq. (\ref{eq:pathInt:DeltaPF}) around it ($\Delta(\vr,\tau)=\Delta_{0}+\eta(\vr,\tau)$). The linear order of  expansion is zero because $\Delta_{0}$ is the saddle point.  The next order gives us the bilinear terms on $\eta$, i.e., correlation of bosonic field $\Delta$ (four-fermion correlation).  Note that here the hamiltonian only has an extreme-short-range ($\delta$) potential, therefore it cannot cover the situation of charged system where long-range Columnb interaction cannot be neglected.  We will discuss this later.  Nevertheless, it is conceivable that a more realistic short-range potential only renormalizes some parameters in the following calculation while leaves the qualitative result unmodified.  

Notice that we can expand the second term in Eq. \ref{eq:pathInt:DeltaPF} for $\hat{G}{}^{-1}=\hat{G}_{0}^{-1}+\hat{K}$
\begin{equation}\label{eq:pathInt:expand}
\tr\ln \hat{G}^{-1}=\tr\ln\hat{G_{0}}^{-1}+\tr(\hat{G_{0}}\hat{K})-\nth{2}\tr(\hat{G_{0}}\hat{K}\hat{G_{0}}\hat{K})+\cdots
\end{equation}
In our case,
\begin{equation}
\hat{K}=\begin{pmatrix}
0&\eta\\
\eta^{*}&0
\end{pmatrix}
\end{equation}
Here the linear terms of $\hat{K}$ or $\eta$ ($\eta^{*}$) are zero as the saddle point condition.  So to the second order, the action is 
\begin{equation}\label{eq:pathInt:DeltaActionGaussian}
S[\Delta_{0},\eta,\eta^{*}]=S[\Delta_{0}]+
	\nth{2g}\tr(\hat{K}\hat{K})+\nth{2}\tr(\hat{G_{0}}\hat{K}\hat{G_{0}}\hat{K})
\end{equation}
Write the last term into the momentum representation
\begin{equation}
\tr(\hat{G_{0}}\hat{K}\hat{G_{0}}\hat{K})=\sum_{q,p}\Tr\br{G_{0}({p})K_{q}G_{0}{}({p-q})K_{-q}}
\end{equation}
Notice that the second ``$\Tr$'' and following ``$\Tr$'' in this section only runs in Nambu spinor space and $q={(\vq,q_{l})}$, $p=(\vp,p_{n})$ are all four momentum, where $q_{l}$ is bosonic Matsubara frequency while $p_{n}$ is fermionic Matsubara frequency.
\begin{equation}
K_{q}=\begin{pmatrix}
0&\eta_{q}\\
\eta^{*}_{-q}&0
\end{pmatrix}
\end{equation}
If we introduce the a new vector 
\begin{equation}
\eta{(q)}=\begin{pmatrix}\eta_{q}\\\eta^{*}_{-q}\end{pmatrix}\qquad
\eta^{\dg}{(q)}=\begin{pmatrix}\eta^{*}_{q}&\eta_{-q}\end{pmatrix}
\end{equation}
the action can be rewritten into a more compact form
\begin{equation}
S[\Delta_{0},\eta,\eta^{*}]=S[\Delta_{0}]+\nth{2}\sum_{q}\Tr\mbr{\eta^{\dg}(q)\mathbf{M(q)}\eta(q)}
\end{equation}
Notice that we can always choose a real $\Delta_{0}$ and therefore $G_{0}{\ _{12}}(p)=G_{0}{\ _{21}}(p)$, we have 
\begin{equation}
\mathbf{M(q)}=
\begin{pmatrix}
\nth{g}+\sum_{p}G_{0}{\ }_{11}(p)G_{0}{\ }_{22}(p-q)&\sum_{p}G_{0}{\ }_{12}(p)G_{0}{\ }_{12}(p-q)\\
\sum_{p}G_{0}{\ }_{12}(p)G_{0}{\ }_{12}(p-q)&\nth{g}+\sum_{p}G_{0}{\ }_{11}(p-q)G_{0}{\ }_{22}(p)
\end{pmatrix}
\end{equation}
The summation over (fermionic) Matsubara frequency of $p_{n}$ can be carried out at zero temperature
\footnote{\label{foot:intro:sum}The summation of Matsubara frequency of function $h(i\omega_{n})$ is carried out by the normal method to multiplying $h(z)$ with fermi distribution function $n_{F}(z)$, and then find all residues with a contour over infinity.  However, due to zero temperature, the  $n_{F}(z)$ only nonzero at the negative singular points of $h(z)$, $-E_{\vk}$ in our case.  (The other singular point $E_{\vk}$ gives $n_{F}(E_{\vk})=0$ for zero temperature.}
\begin{equation}
\begin{split}
M_{11}(q)&=M_{22}(-q)\\
	&=\nth{g}+\sum_{\vp{,}p_{n}}G_{0}{\ }_{11}(p)G_{0}{\ }_{22}(p-q)\\
	&=\nth{g}+\sum_{\vp}\br{\frac{u^{2}u'^{2}}{iq_{l}-E-E'}-\frac{v^{2}v'^{2}}{iq_{l}+E+E'}}
\end{split}
\end{equation}
\begin{equation}
\begin{split}
M_{12}(q)&=M_{21}(q)\\
	&=\sum_{\vp{,}p_{n}}G_{0}{\ }_{12}(p)G_{0}{\ }_{12}(p-q)\\
	&=\sum_{\vp}uvu'v'\br{\nth{iq_{l}+E+E'}-\nth{iq_{l}-E-E'}}
\end{split}
\end{equation}
where $u=u_{\vp}$, $v=v_{\vp}$, $E=E_{\vp}$ and $u'=u_{\vp-\vq}$, $v'=v_{\vk-\vq}$, $E'=E_{\vk-\vq}$.  $u$, $v$, $E$ are as defined usually in BCS literature. 
\begin{equation}
v_{\vk}^{2}=1-u_{\vk}^{2}=\nth{2}\br{1-\frac{\xi_{\vk}}{E_{\vk}}}
\end{equation}
 The $G^{(M)}=\mathbf{M}^{-1}$ is the correlation function of $\eta$ (or $\Delta$) and its poles give the spectrum of collective mode as every  $\eta_{q}$ (or $\Delta_{q}$) involves many fermions moving in a coherent manner.  So the spectrum of collective modes can be determined by $\det{M(\omega,\vq)}=0$ after we analytically continue for the frequency $iq_{l}\rightarrow\omega+i0^{+}$.  
 
For low energy modes, where $\omega,\,\abs{\vq}^{2}\ll\min\bbr{E_{\vk}}$ both are much smaller than $\Delta_{0}$, we can expand $M$ with $\omega$ and $\vq$.  


\subsection{Alternative method to invert Green's function\label{sec:diagonalizeGreen1}}
In the above section, we have inversion of Gorkov green function Eq. (\ref{eq:pathInt:nG}) and it can be invert easily as Eq. (\ref{eq:pathInt:G0}).   Alternatively, we can use a different approach which proves to be more convenient in two-channel problem.  First, we diagonalize $\nG$ with unitary transformation $T$, in momentum space
\begin{equation}
\nG=\mtrx{i\omega_{n}-\xi_{k}&\Delta\\\bar\Delta&i\omega_{n}+\xi_{k}}=T^{\dg}BT
\end{equation}
It is easy to show that such $T$ and $B$ satisfing above equation are
\begin{equation}
T=\mtrx{u_{k}&v_{k}\\-v_{k}^{*}&u_{k}}\qquad{}B=\mtrx{i\omega_{n}+E_{k}&0\\0&i\omega_{n}-E_{k}}
\end{equation}
where $u_{k}^{2}(v_{k}^{2})=\nth{2}(1\pm\xi_{k}/E_{k})$ and $E_{k}$ are conventionally defined quantities in BCS theory.   Actually, this transformation is nothing but Bogoliubov canonical transformation, and $B$ matrix simply describes spectrum of fermionic quasi-particles.  Now it is easy to invert $\nG$
\begin{equation}
G=T^{\dg}B^{-1}T
\end{equation}
Green's function $G$ takes a more conventional form $A/(i\omega_{n}-e_{k})$ without any dependency on frequency in nominator as Eq. (\ref{eq:pathInt:G0}). Matsubara frequency summation over $G_{0}(k)$ in mean-field and $G_{0}(k)G_{0}(k+q)$ in Gaussian order are then fairly straight-forward as in text-book.  
