\section{note of 2009.09.30}
\subsection{Connetion between Two-Body Wave Fucntion and Many-Body Wave Function}
I talked with Shizhong about how he reduce the order parameter in the s-wave scattering wave function in short-distance at real space. (equation 2.61 in \cite{ZhangThesis})  He does not get the $a_s$ directly from 2.60, but by split $\nth{E_k}=\br{\nth{E_k}-\nth{\xi_k}}+\nth{\xi_k}$ and the first difference term is in order of $\nth{k^6}$ for large $k$ and gives negligible contribution in integral. We can neglect the large $k$ part, approximate $\sin{kr}$ in the nominator as $kr$ and that gives us $k^2r$ in the nominator, which is the same as the the normalized gap equation. By comparing with the gap equation, we have $-2r/\pi{a_s}$ and the second part $\int\frac{k\sin{kr}}{\xi_k}dk=\frac{2m}{\hbar^2}\frac{\pi}{2}$.  It does have a $2/\pi$ difference,(maybe just my calculation mistake somewhere), but the structure is correct.  However, you cannot get $a_s$ by comparing with the normalized gap equation.  On the other hand, even without that, it still suggests the correct short-range behavior $\nth{r}\br{1-\frac{r}{\widetilde{a_s}}}$.  Presumably, $F(r)$ is a solution valid for all the region, and the above arguments demonstrates that it reduces to the correct short-range form where long-term effects, i.e. the many-body effects, can be neglected. And it gives the normalization factor which cannot be obtained by solving short-range version of equation.  

So the structure of $F(r)$ is correct, and the factor happens to be $a_s$ because the gap equation and that comes from the two-body description of $T$ matrix. On the other hand, if working backward, we can identify the gap equation and $a_s$ by reasoning that the short-range behavior of $F(r)$ must be proportional to the two-body solution. 

Related to this, the question to ask is what type of the many-body solution reduces to the two-body solution for the Feshbach resonance, especially, the close channel, as exponentially decaying solution, $e^{-r/a^{(c)}}$.  Considering that $a^{(c)}$ is much smaller than the open-channel scattering length $a_s$, the region where it can be treated in the form of $1-r/a$ is very small, $r{\ll}a^{(c)}$; while the two-body solution is expected to be correct for the region much larger $r{\ll}1/k_F$.  But we need to find out how is $F(r)$ and how is $F(k,t=0)$.  The formal solution of $F(k,\omega)$ is in principle available although this needs solving third-order equation and probably only hopeless complicated analytic solution, and it needs to be integrated over both $k$ and $\omega$.  

\input{renorm}
