\subsection{Variation method with the u,v,w}
We start with three hyperfine species a, b, c, where a is the common species in two channel. (a,b) is the open channel while (a,c) is the close channel. And the Hamiltonian is written in the form 
\begin{equation}
\begin{split}
 H=&\sum_\vk\epsilon^a_\vk{}a^+_\vk{}a^{}_\vk+\sum_\vk\epsilon^b_\vk{}b^+_\vk{}b^{}_\vk+\sum_\vk\epsilon^c_\vk{}c^+_\vk{}c^{}_\vk\\
  &+\nth{2}\sum_{\vk\vk'}U_{\vk\vk'}a^+_\vk{}b^+_{-\vk}{}b^{}_{-\vk'}a^{}_{\vk'}
	+\nth{2}\sum_{\vk\vk'}V_{\vk\vk'}a^+_\vk{}c^+_{-\vk}{}c^{}_{-\vk'}a^{}_{\vk'}\\
 &+\nth{2}\sum_{\vk\vk'}Y_{\vk\vk'}a^+_\vk{}b^+_{-\vk}{}c^{}_{-\vk'}a^{}_{\vk'}
	+\nth{2}\sum_{\vk\vk'}Y^*_{\vk\vk'}a^+_{\vk'}{}c^+_{-\vk'}{}b^{}_{-\vk}a^{}_{\vk}
\end{split} 
\end{equation}
By the Hermition condition we have 
\begin{equation}
 U_{\vk'\vk}=U^*_{\vk\vk'},\qquad{} V_{\vk'\vk}=V^*_{\vk\vk'}
\end{equation}
  We start from the ansatz as 
\begin{equation}\label{eq:ansatz}
 \ket{\Psi}=\prod_\vk\br{u_\vk+v_\vk{}a^\dg_\vk{}b^\dg_{-\vk}+w_\vk{}a^\dg_\vk{}c^\dg_{-\vk}}\ket{0}
\end{equation}
Here we require $\abs{u_\vk}^2+\abs{v_\vk}^2+\abs{w_\vk}^2=1$ for normalization.  For all the interaction term, there are two types of contribution,
for example, 
\begin{equation*}
\av{U_{\vk\vk'}a^\dg_\vk{}b^\dg_{-\vk}{}b^{}_{-\vk'}a^{}_{\vk'}}
=\sum_{\vk}U_{\vk\vk}\abs{v_\vk}^2+\sum_{\vk\neq\vk'}U_{\vk\vk'}v^{}_{\vk'}u^*_{\vk'}u^{}_\vk{}v^*_\vk
\end{equation*}
The first term is the Hatree term and the second term is more interesting pairing term.



And the free energy is 
\begin{equation}
 \begin{split}
  &F\equiv\av{H-\mu{}N}\\
    =&\sum(\xi^a_\vk+\xi^b_\vk)\abs{v_\vk}^2+\sum(\xi^a_\vk+\xi^c_\vk)\abs{w_\vk}^2\\
    &+\nth2\sum_{\vk}U_{\vk\vk}\abs{v_\vk}^2+\nth2\sum_{\vk\neq\vk'}U_{\vk\vk'}v^{}_{\vk'}u^*_{\vk'}u^{}_\vk{}v^*_\vk\\
    &+\nth2\sum_{\vk}V_{\vk\vk}\abs{w_\vk}^2
      +\nth2\sum_{\vk\neq\vk'}V_{\vk\vk'}w^{}_{\vk'}u^*_{\vk'}u^{}_\vk{}w^*_\vk\\
    &+\nth2\sum_{\vk}Y_{\vk\vk}w^{}_{\vk}v^*_\vk{}
      +\nth2\sum_{\vk\neq\vk'}Y_{\vk\vk'}w^{}_{\vk'}{u^{*}_{\vk'}}v^*_\vk{}u^{}_\vk\\
    &+\nth2\sum_{\vk}Y^*_{\vk\vk}w^*_{\vk}v^{}_{\vk}{}
      +\nth2\sum_{\vk\neq\vk'}Y^*_{\vk\vk'}w^*_{\vk}{u^{}_{\vk}}v^{}_{\vk'}{}u^{*}_{\vk'}
 \end{split}
\end{equation}
Where 
\begin{equation*}
 \xi^a_\vk=\epsilon^a_\vk-\mu^a,\qquad\xi^b_\vk=\epsilon^b_\vk-\mu^b,\qquad\xi^c_\vk=\epsilon^c_\vk-\mu^b
\end{equation*}
The chemical potential is added to make sure the $n_a=n_b+n_c=\nth{2}n$.
 I drop the Hatree term as this in some sense just shift the chemical potentials as it only relates to the density.  (\emph{Not sure still valid in the two-channel problems, especially for the close-channel.})  Also, I ignore the summation on the second only goes through $\vk\neq\vk'$ as the correction is in the higher order. 
 
Now introduce the parameters $\theta_\vk$, $\phi_\vk$ to include the normalization condition.  
\begin{equation}
 u_{\vk}=\cos\theta_\vk,\qquad{} v_{\vk}=\sin\theta_\vk\cos\phi_\vk,\qquad{}
 w_{\vk}=\sin\theta_\vk\sin\phi_\vk
\end{equation}
We take them as real quantities as those that minimize the free energy are real.(?) Now the free energy can be written as 

\begin{equation}
 \begin{split}
  F=&\sum\xi^{ab}_\vk\sin^2{\theta_\vk}\cos^2\phi_\vk+\sum\xi^{ac}_\vk\sin^2{\theta_\vk}\sin^2\phi_vk\\
    &+\nth2\sum_{\vk\vk'}U_{\vk\vk'}\cos\theta_{\vk'}\sin\theta_{\vk'}\cos\phi_{\vk'}\cos\theta_\vk{}\sin\theta_\vk\cos\phi_\vk\\
    &+\nth2\sum_{\vk\vk'}V_{\vk\vk'}\cos\theta_{\vk'}\sin\theta_{\vk'}\sin\phi_{\vk'}\cos\theta_\vk{}\sin\theta_\vk\sin\phi_\vk\\
    &+\nth2\sum_{\vk\vk'}Y_{\vk\vk'}\cos\theta_{\vk'}\sin\theta_{\vk'}\cos\phi_{\vk'}\cos\theta_\vk{}\sin\theta_\vk\sin\phi_\vk\\
    &+\nth2\sum_{\vk\vk'}Y^*_{\vk\vk'}\cos\theta_{\vk'}\sin\theta_{\vk'}\sin\phi_{\vk'}\cos\theta_\vk{}\sin\theta_\vk\cos\phi_\vk\\
    =&\nth4\sum_\vk\xi^{ab}_\vk(1-\cos2\theta_\vk)(1+\cos2\phi_\vk)+\nth4\sum_\vk\xi^{ac}_\vk(1-\cos2\theta_\vk)(1-\cos2\phi_\vk)\\
    &+\nth{8}\sum_{\vk\vk'}U\sin2\theta_\vk\cos\phi_\vk\sin2\theta_{\vk'}\cos\phi_{\vk'}+\nth{8}\sum_{\vk\vk'}V\sin2\theta_\vk\sin\phi_\vk\sin2\theta_{\vk'}\sin\phi_{\vk'}    \\
    &+\nth{4}\sum_{\vk\vk'}Y\sin2\theta_\vk\cos\phi_\vk\sin2\theta_{\vk'}\sin\phi_{\vk'}    
 \end{split}
\end{equation}
We assume that $Y=Y^*$. From the above equation, we can differentiate it with respect to $\theta_\vk$ and $\phi_\vk$ and set the derivative as 0, therefore minimize free energy. 
\begin{align}
0=&\pdiff{F}{\theta_\vk}\notag\\
 =&\nth{2}\sin2\theta_\vk\mbr{\xi^{ab}_\vk(1+\cos2\phi_\vk)+\xi^{ac}_\vk(1-\cos2\phi_\vk)}\notag\\
 &+\nth2\sum_{\vk'}\cos2\theta_\vk\sin2\theta_{\vk'}\mbr{U\cos\phi_\vk\cos\phi_{\vk'}+V\sin\phi_\vk\sin\phi_{\vk'}+Y\sin(\phi_{\vk'}+\phi_\vk)}\\
 0=&\pdiff{F}{\phi_\vk}\notag\\
 =&-\nth{2}(\xi^{ab}_\vk-\xi^{ac}_\vk)\sin2\phi_\vk(1-\cos2\theta_\vk)\notag\\
 &-\nth4\sum_{\vk'}\sin2\theta_\vk\sin2\theta_{\vk'}\mbr{U\sin\phi_\vk\cos\phi_{\vk'}-V\cos\phi_\vk\sin\phi_{\vk'}-Y\cos(\phi_{\vk'}+\phi_\vk)}
\end{align}
  These two set of equations (for each $\vk$, but decoupled) fully determine the wave-function. 
We introduce two quantities:
\begin{align}
\Delta_\vk^U&=\sum_{\vk'}\sin2\theta_{\vk'}(U_{\vk\vk'}\cos\phi_{\vk'}+Y_{\vk\vk'}\sin\phi_{\vk'})\label{eq:gap1}\\
\Delta_\vk^V&=\sum_{\vk'}\sin2\theta_{\vk'}(V_{\vk\vk'}\sin\phi_{\vk'}+Y_{\vk\vk'}\cos\phi_{\vk'})\label{eq:gap2}
\end{align} 
As we can see eqs.(\ref{eq:gap1},\ref{eq:gap2}) is indeed very similar to the structure of two-body Schr\"{o}‌dinger equation.
If we ‌introduce the Zeeman energy detuning between two channels
\begin{equation}
\eta=\xi^{ab}-\xi^{ac}
\end{equation}
These equations can be written into a more compact form
\begin{align}
\tan2\theta_\vk&=-\frac{\cos\phi_\vk\Delta^U_\vk+\sin\phi_\vk\Delta^V_\vk}{2\xi^{ab}_\vk+2\eta\cos^2\phi_\vk}\label{eq:tan1}\\
\tan\theta_\vk&=-\frac{\sin\phi_\vk\Delta^U_\vk-\cos\phi_\vk\Delta^V_\vk}{2\eta\sin2\phi_\vk}\label{eq:tan2}
\end{align} 


Furthermore, when $k\rightarrow\infty$, from eq. (\ref{eq:tan1}), we see that $\theta\rightarrow0$ as $1/\xi$;  and from eq. (\ref{eq:tan2}), we see that $\sin\phi_\vk\Delta^U=\cos\phi_\vk\Delta^V$ as we assume $\Delta$ varies slowly over $\vk$.  We have 
\begin{align*}
\cos^2\phi_\vk&=\frac{{\Delta^U}^2}{{\Delta^V}^2+{\Delta^U}^2}\\
\sin^2\phi_\vk&=\frac{{\Delta^V}^2}{{\Delta^V}^2+{\Delta^U}^2}
\end{align*}
And 
\[\tan2\theta_\vk=-\frac{({{\Delta^V}^2+{\Delta^U}^2})^{1/2}}{2\xi^{ab}_\vk}\]

Eqs. (\ref{eq:gap1},\ref{eq:gap2}) are similar as those derived from the Green's function method in the eq. (\ref{eq:gapMatrix}), and should be able to renormalized in the similar fashion $\Delta=T(F-G\Delta)$, where in our notation $({F^o,F^c})=(\cos\theta_\vk\sin\theta_\vk\cos\phi_\vk,\cos\theta_\vk\sin\theta_\vk\sin\phi_\vk)$.  The problem, however, is that the eqs. (\ref{eq:tan1},\ref{eq:tan2}) does not present a simple analytic solution about $\theta$ and $\phi$ in terms of $\Delta$ and therefore the gap equations cannot be written into a simple renormalized  equation although they are implicit functions of $\Delta$.
 It is a rather cumbersome process to calculate the integration in renormalized gap equations.  Furthermore, information of the close-channel is close to a simple one-level bound-state is not fully incorporated and the equation might be simpler and has a nicer form if I can manage to do that.  

\subsection{more thoughts}
From eqs. (\ref{eq:gap1},\ref{eq:gap2}), $\Delta^{U,V}_\vk$ varies slowly with $k$ if interaction depends on momentum weakly, at least for low momentum.  Therefore, in the renomalization, they can be taken as constants.  In that case, eqs. (\ref{eq:tan1},\ref{eq:tan2}) determine $\theta_k(\xi_k,\Delta^U,\Delta^V)$ and $\phi_k(\xi_k,\Delta^U,\Delta^V)$, which in turn give two-body wave-function $F^{o,c}_k(\xi_k,\Delta^U,\Delta^V)$.  
With the renomalized gap equation,.  
\begin{equation}\label{eq:renomal1}
\begin{pmatrix}\Delta^U\\\Delta^V\end{pmatrix}=\begin{pmatrix}T_{oo}&T_{oc}\\T_{co}&T_{cc}\end{pmatrix}
\begin{pmatrix}\sum{F^o-\frac{\Delta^U}{2\epsilon}}\\\sum{F^c-\frac{\Delta^V}{2\epsilon+\eta}}\end{pmatrix}
\end{equation}
and the number equation, should give us three parameters in the problems: $\Delta^{U,V}$ and $\mu$.  The close-channel infomation is incorporated into the $T$-matrix.  The problem is more about the computation difficulty as there is no simple analytic solution for $F^{o,c}$, therefore, eq. (\ref{eq:renomal1}) cannot be done easily.

What happened in the broad-resonance limit? Or very BEC/BCS end? 

\subsection{T-matrix}
Follow \cite{JacksonNarrow}, the bare interaction $V$ should have the form \footnote{notice the some change of notation}
\begin{equation}
V(r)=\frac{V_s(r)+3V_t(r)}{4}+\mbr{V_t(r)-V_s(r)}\mathbf{S_1}\cdot\mathbf{S_2}
\end{equation}
we can establish the T-matrix from $V$.
\begin{equation}
 {\fmtrx{T_{cc}}{T_{co}}{T_{oc}}{T_{oo}}}^{-1}={\fmtrx{V_{cc}}{V_{co}}{V_{oc}}{V_{oo}}}^{-1}-{\fmtrx{G_{c}}{0}{0}{G_{o}}}
\end{equation}
For 0-temperature, pair propagators $G_o$ and $G_c$ are
\begin{equation}
 G_o(\omega,\vK,\vq)=\nth{\omega+i\delta-\frac{K^2}{4m}-\frac{q^2}{m}}
\end{equation}
\begin{equation}
 G_c(\omega,\vK,\vq,B)=\nth{\omega+i\delta-\eta(B)-\frac{K^2}{4m}-\frac{q^2}{m}}
\end{equation}
where $E_{th}(B)$ is the detuning, depending on magnatic field $B$. Here we can break it down into two steps. First, introduce 
 \begin{equation}
 {\fmtrx{U_{cc}}{U_{co}}{U_{oc}}{U_{oo}}}^{-1}={\fmtrx{V_{cc}}{V_{co}}{V_{oc}}{V_{oo}}}^{-1}-{\fmtrx{G^{vac}}{0}{0}{G^{vac}}}
\end{equation}
where $G^{vac}(q)=(i\delta-q^2/m)^{-1}$ is the vacuum pair propagator ignoring the hyperfine splitting at $\omega=0$ and no center momentum $\vK$.  Furthermore, when the close-channel resonnant state is close to threshold and well-seperated from other discrete levels, the effective interaction is separable.  So 
\begin{equation}
 U(\vq',\vq)=\frac{4\pi}{m}\mbr{\frac{a_s+3a_t}{4}+(a_t-a_s)\mathbf{S_1}\cdot\mathbf{S_2}}g(q')g(q)
\end{equation}
$g(q)\rightarrow0$ for $qr_C\rightarrow\infty$ where $r_C$ is the interaction range.  But This can be projected to the hyperfine-spin space and therefore two-channel.  
\begin{equation}
 {\fmtrx{U_{cc}}{U_{co}}{U_{oc}}{U_{oo}}}=
\frac{4\pi}{m}\mbr{\fmtrx{\frac{c_7a_s+a_t}{1+c_7}}{\frac{a_t-a_s}{\sqrt{1+c_7}\sqrt{1+c_9}}}
{\frac{a_t-a_s}{\sqrt{1+c_7}\sqrt{1+c_9}}}{\frac{c_9a_s+a_t}{1+c_9}}}
\end{equation}
For example, $\ket{9/2,-9/2}$, $\ket{9/2,-7/2}$, $\ket{7/2,-7/2}$ of ${}^{40}K$ at resonance $B=201.6$, $c_7=14.9$ and $c_9=0.059$ Note that both $c_7$ and $c_9$ depends on B.  

The second step deals with the influence of $B$ in the theshold $E_{th}$ as well as the energy dependence of $G$. 
 \begin{equation}
  {\fmtrx{T_{cc}}{T_{co}}{T_{oc}}{T_{oo}}}^{-1}={\fmtrx{U_{cc}}{U_{co}}{U_{oc}}{U_{oo}}}^{-1}-{\fmtrx{\Delta{}G_c}{0}{0}{\Delta{}G_o}}
\end{equation}
where $\Delta{}G_{o/c}=G_{o,c}(\omega,\vK,\vq,B)-G^{vac}(q)$.  Using the seperable properties of $U$, we can concentrate the $\vq$ dependence on two quantities and this leaves us a simple two-by-two algebra matrix equation.  
\begin{equation}
\Pi_{o,c}(\omega,\vK,B)=\int\frac{d^3q}{(2\pi)^3}\Delta{}G_{o,c}g^2(q)                  
\end{equation}
where for the contact interaction with $r_C=0$, we find $\Pi_o(\omega,\vK)=-im^{3/2}\sqrt{\omega-K^2/(4m)}$ and $\Pi_c(\omega,\vK,B)=\Pi_o(\omega-E_{th}(B),\vK)$
Especially, for $\omega=0$ and no central mometum $\vK$, $\Pi_o=0$ and $\Pi_c=\sqrt{-\eta(B)}$
\begin{gather}\label{eq:T}
 T_{cc}=\frac{U_{cc}}{1-U_{cc}\Pi_c}\\
T_{oc}=T_{co}=\frac{U_{oc}}{1-U_{cc}\Pi_c}\\
T_{oo}=U_{oo}+\frac{U_{oc}^2\Pi_c}{1-U_{cc}\Pi_c}
\end{gather}
comparing this with the commonly used formula 
\begin{equation}
 T_{oo}=\frac{4\pi{}a_{bg}}{m}\br{1-\frac{\Delta{}B}{B-B_0}}
\end{equation}
We find the resonance position $B_0$ satisfies
\begin{equation}
 1-U_{cc}(B_0)\Pi_c(B_0)=0
\end{equation}
And other quantities, such as $a_s$, $a_t$ can be expressed with the experimental quantities. 

However, it is still not clear to me how to really map broad /narrow resonance into the many-body eq.(\ref{eq:renomal1}) in a calculable sense.  The criteria of broad resonance as in \cite{JacksonNarrow} is   
\begin{equation}\label{eq:broadCriteria}
\Delta\mu\Delta{}B\gg\frac{k_F}{ma_{bg}}
\end{equation}


\subsection{rescale with Fermi momemtum/energy}
If we rescale renormalized gap equation eq. \ref{eq:renomal1} and the number equation with the Fermi momentum/energy, we have 
\begin{equation}\label{eq:renormal2}
\begin{pmatrix}\widetilde\Delta^U\\\widetilde\Delta^V\end{pmatrix}=
8\pi{a}{k_F}\begin{pmatrix}1&T_{oc}/T_{oo}\\T_{co}/T_{oo}&T_{cc}/T_{oo}\end{pmatrix}
\int\widetilde{k}^2d\widetilde{k}
\begin{pmatrix}
\nth{2}\sin2\theta_{k}\cos\phi_k-\frac{\widetilde\Delta^U}{2\widetilde\epsilon}\\
\nth{2}\sin2\theta_{k}\sin\phi_k-\frac{\widetilde\Delta^U}{2\widetilde\epsilon+\widetilde{\eta}}
\end{pmatrix}
\end{equation}
and rescaled number equation
\begin{equation}
 \int\widetilde{k}^2\sin^2\theta_kd\widetilde{k}=\nth{3}
\end{equation}
We can find the criteria of broad resonance (eq. \ref{eq:broadCriteria}) becomes 
\begin{equation}
 ak_F\widetilde{\eta}\gg1 
\end{equation}
Here we use $a=a_{bg}(1+\Delta_B/(B-B_0)$,  ignoring constant $1$ around the resonance, and also use the fact that rougly $\eta=\Delta\mu(B-B_0)$. At the broad limit, term $\frac{\widetilde\Delta^U}{2\widetilde\epsilon+\widetilde{\eta}}$ of the second integration in eq. \ref{eq:renormal2} gives a negligible contribution when $\sin2\theta_k$ is substantial.  So a simple solution is to put $\cos\phi_k\approx1$ while $\sin\phi_k\approx0$ for where $\sin2\theta_k$ is substantial (i.e. the particle is concentrated in open-channel).  Therefore, we reduce the two-channel problems into one-channel problem, omitting the close-channel. Here, we can see the interplaying between fermi energy and the two-body quantities, whether eq. \ref{eq:renormal2} can be reduced to a single-channel problem is due to the size of $\widetilde{\eta}$, which is determined by the ratio of the deturning and Fermi energy.  